Trends of SDR in Thessaloniki

### 2023-06-26 Article.tex
Commit 2023-06-26 18:17

@@

The SDR is equivalent to the whole sky Global radiation, also refered as
Global Horizontal Irradiance (GHI), and was obtained with a horizontal
leveled, CM-21 pyranometer. SDR data spans the period of 1993-04-12 to
2011-03-31. In some algorithms we used as auxiliary data, the direct
beam radiation (DNI) for comparisons, obtained by a CHP-1 pyrheliometer,
with data availability from Inf to -Inf.

@@

Due to a significant measurement uncertainty near, the horizon, we have
to exclude all measurements with SZA greater than \(85^\circ\).
Moreover, due to some obstructions around the site (hills and
buildings), we excluded data with Azimuth angle between \(35^\circ\) and
\(120^\circ\) with SZA greater than \(80^\circ\). On the latter
instances, Sun is systematically, not visible by the instrument's
location. To make the measurements comparable throughout the dataset, we
adjusted all 1-minute radiometric values to the mean Sun - Earth
distance. Subsequently, we made all measurements relative to the Total
Solar Irradiance (TSI) at \(1 \text{au}\), in order to compensate for
the Sun's intensity variability, using a homogenized time series of
satellite TSI observations. The TSI data we use, is a combination of
data from NOAA \citep{Coddington2005} (for 1993-04-12 - 2011-03-31) and
adjusted data from \citet{TSIStsi} (for - ). As a result, we can present
all radiation data as a fraction of Sun's TSI.

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2048}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1928}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2169}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3855}}@{}}
\caption{\label{tab:trendtable}Trends of daily means by sky conditions.
}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend statistical signif. {[}\%{]}
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend statistical signif. {[}\%{]}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
0.4221 & 5.871e-06 & All sky cond. & 100 \\
0.3871 & 0.0001123 & Clear sky cond. & 99.99 \\
0.415 & 0.002237 & Cloudy cond. & 99.78 \\
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2361}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2222}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1250}}@{}}
\caption{\label{tab:trendseasontable}Trends of daily means by sky
conditions for the seasons of the year. (continued
below)}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Season
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Season
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
0.8014 & 0.1606 & All sky cond. & Winter \\
-0.1999 & 0.5397 & All sky cond. & Spring \\
0.2777 & 0.09127 & All sky cond. & Summer \\
0.3768 & 0.2006 & All sky cond. & Autumn \\
0.9574 & 0.1081 & Clear sky cond. & Winter \\
-0.4227 & 0.2207 & Clear sky cond. & Spring \\
0.0931 & 0.6638 & Clear sky cond. & Summer \\
0.3233 & 0.3255 & Clear sky cond. & Autumn \\
-0.4354 & 0.4924 & Cloudy cond. & Winter \\
0.8353 & 0.04263 & Cloudy cond. & Spring \\
0.7051 & 0.05457 & Cloudy cond. & Summer \\
0.3708 & 0.2357 & Cloudy cond. & Autumn \\
\end{longtable}

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{0.4444}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Trend statistical signif. {[}\%{]}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
83.94 \\
46.03 \\
90.87 \\
79.94 \\
89.19 \\
77.93 \\
33.62 \\
67.45 \\
50.76 \\
95.74 \\
94.54 \\
76.43 \\
\end{longtable}

@@

Our result for all-sky condition (\(0.42\%/year\)), reaffirm the
previous results of \citet{Bais2013} for the site. The increase of this
trend, shows that the phenomenon and probably the causes have been
amplified.

\ldots.. Also, the trend of \(0.41\%/year\) for cloud-sky condition
indicate the major part that clouds play on the \ldots..

@@

\bibliography{references.bib}

>>>>

Cloud ``shrinking'' and ``optical thinning'' in the ``dimming'' period
and a subsequent recovery in the ``brightening'' period over China

aerosols not only strengthen but also weaken the growth of clouds with
respect to their coverage and optical thickness, depending on the levels
of pollution and the associated amounts of aerosols as postulated in a
conceptual framework (Wild 2009a, 2012, Yang et al 2012).

@@

The SDR is equivalent to the whole sky Global radiation, also refered as
Global Horizontal Irradiance (GHI), and was obtained with a horizontal
leveled, CM-21 pyranometer. SDR data spans the period of 1993-04-12 to
2023-05-31. In some algorithms we used as auxiliary data, the direct
beam radiation (DNI) for comparisons, obtained by a CHP-1 pyrheliometer,
with data availability from 2016-04-01 to 2023-05-31.

@@

Due to a significant measurement uncertainty near, the horizon, we have
to exclude all measurements with SZA greater than \(85^\circ\).
Moreover, due to some obstructions around the site (hills and
buildings), we excluded data with Azimuth angle between \(35^\circ\) and
\(120^\circ\) with SZA greater than \(80^\circ\). On the latter
instances, Sun is systematically, not visible by the instrument's
location. To make the measurements comparable throughout the dataset, we
adjusted all 1-minute radiometric values to the mean Sun - Earth
distance. Subsequently, we made all measurements relative to the Total
Solar Irradiance (TSI) at \(1 \text{au}\), in order to compensate for
the Sun's intensity variability, using a homogenized time series of
satellite TSI observations. The TSI data we use, is a combination of
data from NOAA \citep{Coddington2005} (for 1993-04-12 - 2023-03-31) and
adjusted data from \citet{TSIStsi} (for 2023-03-31 - 2023-05-31). As a
result, we can present all radiation data as a fraction of Sun's TSI.

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2048}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1928}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2169}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3855}}@{}}
\caption{\label{tab:trendtable}Trends of daily means by sky conditions.
}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend statistical signif. {[}\%{]}
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend statistical signif. {[}\%{]}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
0.381 & 3.479e-21 & All sky cond. & 100 \\
0.3605 & 1.068e-16 & Clear sky cond. & 100 \\
0.3472 & 8.968e-09 & Cloudy cond. & 100 \\
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2361}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2222}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1250}}@{}}
\caption{\label{tab:trendseasontable}Trends of daily means by sky
conditions for the seasons of the year. (continued
below)}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Season
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Season
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
0.7215 & 0.001209 & All sky cond. & Winter \\
0.1679 & 0.1083 & All sky cond. & Spring \\
0.128 & 0.08705 & All sky cond. & Summer \\
0.4239 & 0.006659 & All sky cond. & Autumn \\
0.8715 & 0.000269 & Clear sky cond. & Winter \\
0.09719 & 0.3923 & Clear sky cond. & Spring \\
-0.02369 & 0.7972 & Clear sky cond. & Summer \\
0.3583 & 0.02996 & Clear sky cond. & Autumn \\
-0.02581 & 0.9335 & Cloudy cond. & Winter \\
0.3557 & 0.06914 & Cloudy cond. & Spring \\
0.442 & 0.004988 & Cloudy cond. & Summer \\
0.4776 & 0.01955 & Cloudy cond. & Autumn \\
\end{longtable}

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{0.4444}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Trend statistical signif. {[}\%{]}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
99.88 \\
89.17 \\
91.29 \\
99.33 \\
99.97 \\
60.77 \\
20.28 \\
97 \\
6.646 \\
93.09 \\
99.5 \\
98.04 \\
\end{longtable}

@@

Our result for all-sky condition (\(0.38\%/year\)), reaffirm the
previous results of \citet{Bais2013} for the site. The increase of this
trend, shows that the phenomenon and probably the causes have been
amplified.

\ldots.. Also, the trend of \(0.35\%/year\) for cloud-sky condition
indicate the major part that clouds play on the \ldots..

@@

\bibliography{/home/athan/LIBRARY/A\_Atmosphere/A\_Atmosphere.bib}
